Automatically Splitting a Staged Lambda Calculus

### 2015-07-10 paper/splitting.tex
expand on the importance of ground in 4.5

The \texttt{partition} function in the quickselect example in
\ref{sec:exampleQS} is an example of such a function that contains no
second-stage computations, but, if not defined within a $\pure$
annotation, would cause splitting to generate a recursive resumer.

\TODO consider expanding, based on comments from reviews

>>>>

An illustrative example is the \texttt{partition} function in the quickselect
example of \ref{sec:exampleQS}. If \texttt{partition} were defined at \bbonem\
instead of \bbonep, then (like \texttt{qs}) it would split into two functions
\texttt{partition1} and \texttt{partition2}, the latter of which recursively
computes the (trivial) second-stage component of \texttt{partition}'s result.
Moreover, \texttt{qs2} would call \texttt{partition2}, just as \texttt{qs1}
calls \texttt{partition1}:
\begin{lstlisting}
2`fun qs2 (p : tree, k : int) : int =
... | Branch (i,h,p1,p2) =>
  let val () = partition2 ((),()) in
  case compare k i of ...
\end{lstlisting}
By explicitly marking that \texttt{partition} has no second-stage computations,
we avoid both generating the resumer \texttt{partition2}, and calling it in
\texttt{qs2}.

\TODO somebody should read the new text about partition
